Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY

### 2016-01-12 Manuscript/Manuscript.Rnw
fixed tables

\documentclass[a4paper,man,apacite,natbib,12pt,longtable]{apa6}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle

@@

<<setup_Data_9,include=FALSE,cache=FALSE>>=

@@

<<setup_Data_10,include=FALSE,cache=FALSE>>=

@@

<<setup_Data_11,include=FALSE,cache=FALSE>>=

@@

<<setup_summarystats,include=FALSE,cache=FALSE>>=

@@

<<setup_Reliability,include=FALSE,cache=FALSE>>=

@@

### Export Cousin Cor
capture.output(xtable(cor_1star(matrix_b,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_b.tex"))
capture.output(xtable(cor_1star(matrix_g,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_g.tex"))
capture.output(xtable(cor_1star(matrix_z,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_z.tex"))
@
<<measurement,include=FALSE,cache=FALSE>>=
# G1
## mplus
### Run
#### runModels(directory =paste0(directory,"/Common/content/mplusautomation/MplusG1"))
ModelSummaries_Mplus<-extractModelSummaries(target = paste0(directory,"/Common/content/mplusautomation/MplusG1"))
### Clean Up
ModelSummaries_Mplus[,4]<-NULL;ModelSummaries_Mplus[,3]<-NULL;ModelSummaries_Mplus[,2]<-NULL;ModelSummaries_Mplus[,1]<-NULL;ModelSummaries_Mplus[,23]<-NULL
### Export
capture.output(stargazer(ModelSummaries_Mplus,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_gen1measurement.tex"))

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=FALSE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
notes.append = TRUE
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

@@

# Summary Stats by Race and Gender
capture.output(latex(
  tabular((Heading()*( 1 +RowFactor(CSEX)*RowFactor(Race)+ RowFactor(CSEX)+ RowFactor(Race) )~(Heading("AFI")*AFI_G2*(Mean + Sd))), 
          data = Gen2AFIConcor_2),
  numeric.dollar=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_AFIRACEGENDER.tex"))
@
<<setup_tables,include=FALSE,cache=FALSE>>=
# Summary Stats G1
## Manage data
### Import
df <- merge(Gen1AFIConcor,birthweight_fb,by="MCASEID",all=T)
nlsyextract <- read.csv(paste0(directory,"/Common/content/data/nlsyextract.csv"))
###
### Clean
nlsyextract$IDC1[nlsyextract$IDC1 <= 0  ] <- 0
nlsyextract$IDC1[nlsyextract$IDC1 > 0  ] <- 1
nlsyextract$SiblinginSample <-nlsyextract$IDC1
nlsyextract$IDC1 <- NULL
nlsyextract[nlsyextract< 0  ] <- NA
nlsyextract$month<-nlsyextract$Q1.3_A.M 
nlsyextract$month<- paste("0",nlsyextract$Q1.3_A.M,sep="")
nlsyextract$month[nlsyextract$month == 010 ] <- 10
nlsyextract$month[nlsyextract$month == 011 ] <- 11
nlsyextract$month[nlsyextract$month == 012 ] <- 12
nlsyextract$Age<-as.numeric(as.Date(paste(df$YRB,"-06-15",sep=""), format='%Y-%m-%d')-as.Date(paste("19",nlsyextract$Q1.3_A.Y,"-",nlsyextract$month,"-15",sep=""), format='%Y-%m-%d'))/365.25
summarystats_g1<-data.frame(nlsyextract$SiblinginSample,nlsyextract$Age,df$Intel_G1,df$AFI_G1,nlsyextract$SAMPLE_SEX)
###
### Sibling in sample?
#### Gen2AFIConcor$MCASEID<-birthweight$MCASEID
#### data=Gen2AFIConcor
#### data$dup<-0
#### for (x in 1:length(data[,1])) {
#### for (y in 1:length(data[,1])) {
#### if (data$MCASEID[x]==data$MCASEID[y]) data$dup[x]= data$dup[x]+1 }}
#### write.table(data, file = paste0(directory,"/Common/content/data/g2sibinsample.csv"), append = FALSE)
Gen2AFIConcor<- read.table(paste0(directory,"/Common/content/data/g2sibinsample.csv"), header=TRUE, quote="\"")
Gen2AFIConcor$SiblinginSample<-1
Gen2AFIConcor$SiblinginSample[Gen2AFIConcor$dup == 1 ]<- 0
summarystats_g2 <- merge(categories_g2,Gen2AFIConcor,by="CASEID",all=T)
summarystats_g2$zIntel_G2<-scale(summarystats_g2$Intel_G2)
summarystats_g2 <- merge(summarystats_g2,birthweight_2,by="CASEID",all=T)
##
## Capture output
capture.output(latex(
  tabular(((Heading("Mother Age at Birth")*nlsyextract.Age + Heading("Standardized AFQT")*df.Intel_G1 + Heading("AFI")*df.AFI_G1 ) ~ Heading("Has Sibling in NLSY?")*(Mean + Sd)*Heading()*( 1 + RowFactor(nlsyextract.SiblinginSample) )), data = summarystats_g1),
  numeric.dollar=TRUE,na.blank=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_sibinsampleg1.tex"))

@@

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
\subsection{Research Design}
\input{../Common/content/writing/design.tex}
%
% Sample
\subsection{Sample}
\input{../Common/content/writing/subjects.tex}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/writing/tetrad.tex}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
% Age at First Intercourse
\subsection{Measures}
\input{../Common/content/writing/AFI.tex}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Smoothed Density Plots of AFI by Race and Sex}
\label{plot_afi_by_race_sex}
\begin{center}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".65\\paperwidth",warning=FALSE>>=
# Data Prep
dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
names(dataframe)<- c("CASEID","MCASEID","Race","SEX","AFI","Intel")

@@

ggplot(dataframe, aes(x=AFI, colour=RacebySEX, group=RacebySEX, linetype = RacebySEX))+ geom_density(fill=NA,adjust=2)+ theme_min(size=10)+  
    theme(legend.position="bottom",
          legend.justification=c(1, 0.5),
          legend.text=element_text(size=6),
          legend.key = element_rect(fill = 'white', size = 0.5),
          legend.title = element_blank()) +   
    xlab("AFI") + 
    ylab("Density") +
    scale_colour_manual(values= c("#56B4E9","#56B4E9", "#009E73", "#009E73", "#CC79A7", "#CC79A7")) +
    coord_cartesian(ylim=c(0,0.25), xlim=c(12,25)) +
    scale_linetype_manual(values=c(1,2,1,2,1,2))
  @
\end{center}
\end{minipage}
%
% Intelligence
\input{../Common/content/writing/intelligence.tex}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
<<calculationalphadif,cache=FALSE,include=FALSE>>=
# Intelligence
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /(sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
#AFI
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
r.diff.afi <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
Our design assumes that the difference scores of our measures are reliable. We've reported the test-retest reliability of Gen2 intelligence and Gen1 AFI in earlier sections. Here, we report the test-retest reliability of the pairwise differences of those measures. 
\subsubsection{AFI} Comparing sibling differences in AFI as reported in 1983 and 1984 (n = 783 pairs) we found a moderate correlation (r = .76). The sample of sibling pairs with complete information in 1985 was too small (n = 12 pairs) to compare to the other two years. Regardless, sibling differences in self-reported AFI appear satisfactory for research purposes. We note that the common concern with unreliability of difference scores is at least partially mitigated when the separate scores defining the differences are reliable themselves. Because we could not estimate test-retest reliabilities for Generation 2, we calculated the reliability using Lord's equation (\citeyear{Lord1963}). Generation 2 Mean AFI difference scores were also moderately reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.

@@

%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/writing/results.tex}
%
% Between-Family
\subsection{Between-Family Analyses}
\input{../Common/content/writing/results_between.tex}
%
% Within-Family
\subsection{Within-Family Analyses}
\input{../Common/content/writing/results_within.tex}
%
%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/writing/discussion.tex}

%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
%%%%%%%%%%%% Appendix %%%%%%%%%%%%
   \begin{landscape} \appendix\label{appen}
  %
  % Age 10.5 Replication
  \section{Age 10.5 Replication}\label{appen10}
  %% Between-Family

@@

  %
\begin{landscape}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 1: Age at First Intercourse vs. Intelligence}
\label{plot_gen1_afi}
\begin{center}
<<plot_gen1_afi,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
library(ggplot2)
library(gtable)
library(grid)
library(gridExtra)
library(NlsyLinks)
# Gen 1 Plot
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen1AFIConcor
dsOutcomes$Sex<-testretest$SEX
dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsD <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c("Intel_G1","AFI_G1","Sex"))
dsD$DIF_G<-#abs
  (dsD$Intel_G1_S1-dsD$Intel_G1_S2)
dsD$DIF_A<-#abs
  (dsD$AFI_G1_S1-dsD$AFI_G1_S2)
#m<-data.frame(Gen2AFIConcor$Intel_G2,Gen2AFIConcor$AFI_G2)

shading<-c("navy","dodgerblue4","dodgerblue3","dodgerblue2","lightsteelblue1","dodgerblue2","dodgerblue3","dodgerblue4","navy")
shading<-c("firebrick4",#"firebrick3","firebrick2",
           "firebrick1",#"mediumvioletred",
             "dodgerblue1",#"dodgerblue2","dodgerblue3",
           "dodgerblue4")
max_val <- max(abs(dsD$DIF_G),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))
##############
ggplot(dsD, aes(y=AFI_G1_S1, x=Intel_G1_S1,colour=(DIF_G))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.1, h = 0.5)) +
  scale_colour_gradientn(name="Sibling \nDifferences \nin AFQT",colours=shading,values=values,rescaler = function(x, ...) x, oob = identity)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=16,face="bold"))+ 
  ylab("Age at First Intercourse") +
  xlab("AFQT (Z Score)") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")

@
\end{center}
\end{minipage}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 2: Age at First Intercourse vs. Intelligence}
\label{plot_gen2_afi}
\begin{center}
<<plot_gen2_afi,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=

# Gen 2 Plot
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen2AFIConcor_3

dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsOutcomes<-dsOutcomes[!is.na(dsOutcomes$SubjectTag),]
ds2D <-dsOutcomes#
max_val <- max(abs(ds2D$Intel_G1),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))
##############
ggplot(ds2D, aes(y=AFI_G2, x=Intel_G2,colour=(Intel_G1))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.01, h = 0.5)) +
  scale_color_gradientn(values=values,rescaler = function(x, ...) x, oob = identity,name="Maternal\n AFQT",colours=shading)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=16,face="bold"))+ 
  ylab("Age at First Intercourse") +
  xlab("General Cognitive Ability") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")

@
\end{center}
\end{minipage}\end{landscape}
\end{document}

>>>>

\documentclass[a4paper,man,apacite,natbib,12pt,longtable,mask]{apa6}
\usepackage{../Common/style/Mason}
\usepackage{listings}
\usepackage{inconsolata}

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{%Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle

@@

<<setup_Data_9,include=FALSE,cache=TRUE>>=

@@

<<setup_Data_10,include=FALSE,cache=TRUE>>=

@@

<<setup_Data_11,include=FALSE,cache=TRUE>>=

@@

<<setup_summarystats,include=FALSE,cache=TRUE>>=

@@

<<setup_Reliability,include=FALSE,cache=TRUE>>=

@@

### Export Cousin Cor
capture.output(xtable(cor_1star(matrix_b,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_b.tex"))
capture.output(xtable(cor_1star(matrix_g,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_g.tex"))
capture.output(xtable(cor_1star(matrix_z,2,.01,include.n=TRUE)),file=paste0(directory,"/Common/content/tables/table_diffintreliable_z.tex"))
@
<<measurement,include=FALSE,cache=TRUE>>=
# G1
## mplus
### Run
#### runModels(directory =paste0(directory,"/Common/content/mplusautomation/MplusG1"))
ModelSummaries_Mplus<-extractModelSummaries(target = paste0(directory,"/Common/content/mplusautomation/MplusG1"))
### Clean Up
ModelSummaries_Mplus[,4]<-NULL;ModelSummaries_Mplus[,3]<-NULL;ModelSummaries_Mplus[,2]<-NULL;ModelSummaries_Mplus[,1]<-NULL;ModelSummaries_Mplus[,23]<-NULL
### Export
capture.output(stargazer(ModelSummaries_Mplus,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_gen1measurement.tex"))

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=TRUE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
notes.append = TRUE
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

@@

# Summary Stats by Race and Gender
capture.output(latex(
  tabular((Heading()*( 1 +RowFactor(CSEX)*RowFactor(Race)+ RowFactor(CSEX)+ RowFactor(Race) )~(Heading("AFI")*AFI_G2*(Mean + Sd))), 
          data = Gen2AFIConcor_2),
  numeric.dollar=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_AFIRACEGENDER.tex"))
@
<<setup_tables,include=FALSE,cache=TRUE>>=
# Summary Stats G1
## Manage data
### Import
df <- merge(Gen1AFIConcor,birthweight_fb,by="MCASEID",all=T)
nlsyextract <- read.csv(paste0(directory,"/Common/content/data/nlsyextract.csv"))
###
### Clean
nlsyextract$IDC1[nlsyextract$IDC1 <= 0  ] <- 0
nlsyextract$IDC1[nlsyextract$IDC1 > 0  ] <- 1
nlsyextract$SiblinginSample <-nlsyextract$IDC1
nlsyextract$IDC1 <- NULL
nlsyextract[nlsyextract< 0  ] <- NA
nlsyextract$month<-nlsyextract$Q1.3_A.M 
nlsyextract$month<- paste("0",nlsyextract$Q1.3_A.M,sep="")
nlsyextract$month[nlsyextract$month == 010 ] <- 10
nlsyextract$month[nlsyextract$month == 011 ] <- 11
nlsyextract$month[nlsyextract$month == 012 ] <- 12
nlsyextract$Age<-as.numeric(as.Date(paste(df$YRB,"-06-15",sep=""), format='%Y-%m-%d')-as.Date(paste("19",nlsyextract$Q1.3_A.Y,"-",nlsyextract$month,"-15",sep=""), format='%Y-%m-%d'))/365.25
summarystats_g1<-data.frame(nlsyextract$SiblinginSample,nlsyextract$Age,df$Intel_G1,df$AFI_G1,nlsyextract$SAMPLE_SEX)
###
### Sibling in sample?
#### Gen2AFIConcor$MCASEID<-birthweight$MCASEID
#### data=Gen2AFIConcor
#### data$dup<-0
#### for (x in 1:length(data[,1])) {
#### for (y in 1:length(data[,1])) {
#### if (data$MCASEID[x]==data$MCASEID[y]) data$dup[x]= data$dup[x]+1 }}
#### write.table(data, file = paste0(directory,"/Common/content/data/g2sibinsample.csv"), append = FALSE)
Gen2AFIConcor<- read.table(paste0(directory,"/Common/content/data/g2sibinsample.csv"), header=TRUE, quote="\"")
Gen2AFIConcor$SiblinginSample<-1
Gen2AFIConcor$SiblinginSample[Gen2AFIConcor$dup == 1 ]<- 0
summarystats_g2 <- merge(categories_g2,Gen2AFIConcor,by="CASEID",all=T)
summarystats_g2$zIntel_G2<-scale(summarystats_g2$Intel_G2)
summarystats_g2 <- merge(summarystats_g2,birthweight_2,by="CASEID",all=T)
##
## Capture output
capture.output(latex(
  tabular(((Heading("Mother Age at Birth")*nlsyextract.Age + Heading("Standardized AFQT")*df.Intel_G1 + Heading("AFI")*df.AFI_G1 ) ~ Heading("Has Sibling in NLSY?")*(Mean + Sd)*Heading()*( 1 + RowFactor(nlsyextract.SiblinginSample) )), data = summarystats_g1),
  numeric.dollar=TRUE,na.blank=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_sibinsampleg1.tex"))

@@

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
\subsection{Research Design}
\input{../Common/content/writing/design.tex}
%
% Sample
\subsection{Sample}
\input{../Common/content/writing/subjects.tex}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/writing/tetrad.tex}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
% Age at First Intercourse
\subsection{Measures}
\input{../Common/content/writing/AFI.tex}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Smoothed Density Plots of AFI by Race and Sex}
\label{plot_afi_by_race_sex}
\begin{center}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=TRUE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".65\\paperwidth",warning=FALSE>>=
# Data Prep
dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
names(dataframe)<- c("CASEID","MCASEID","Race","SEX","AFI","Intel")

@@

ggplot(dataframe, aes(x=AFI, colour=RacebySEX, group=RacebySEX, linetype = RacebySEX))+ geom_density(fill=NA,adjust=2)+ theme_min(size=10)+  
    theme(legend.position="bottom",
          legend.justification=c(1, 0.5),
          legend.text=element_text(size=6),
          legend.key = element_rect(fill = 'white', size = 0.5),
          legend.title = element_blank()) +   
    xlab("AFI") + 
    ylab("Density") +
    scale_colour_manual(values= c("#56B4E9","#56B4E9", "#009E73", "#009E73", "#CC79A7", "#CC79A7")) +
    coord_cartesian(ylim=c(0,0.25), xlim=c(12,25)) +
    scale_linetype_manual(values=c(1,2,1,2,1,2))
  @
\end{center}
\end{minipage}
%
% Intelligence
\input{../Common/content/writing/intelligence.tex}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
<<calculationalphadif,cache=TRUE,include=FALSE>>=
# Intelligence
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /(sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
#AFI
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
r.diff.afi <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
Our design assumes that the difference scores of our measures are reliable. We've reported the test-retest reliability of Gen2 intelligence and Gen1 AFI in earlier sections. Here, we report the test-retest reliability of the pairwise differences of those measures. 
\subsubsection{AFI} Comparing sibling differences in AFI as reported in 1983 and 1984 (n = 783 pairs) we found a moderate correlation (r = .76). The sample of sibling pairs with complete information in 1985 was too small (n = 12 pairs) to compare to the other two years. Regardless, sibling differences in self-reported AFI appear satisfactory for research purposes. We note that the common concern with unreliability of difference scores is at least partially mitigated when the separate scores defining the differences are reliable themselves. Because we could not estimate test-retest reliabilities for Generation 2, we calculated the reliability using Lord's equation (\citeyear{Lord1963}). Generation 2 Mean AFI difference scores were also moderately reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.

@@

%%%%%%%%%%%% Results %%%%%%%%%%%%
\section{Results}
\input{../Common/content/writing/results.tex}
%
% Between-Family
\subsection{Between-Family Analyses}
\input{../Common/content/writing/results_between.tex}
%
\begin{landscape}\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 2: Age at First Intercourse vs. Intelligence}
\label{plot_gen2_afi}
\begin{center}
<<plot_gen2_afi,fig=TRUE,echo=FALSE,cache=TRUE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
library(ggplot2)
library(gtable)
library(grid)
library(gridExtra)
library(NlsyLinks)
# Gen 2 Plot
shading<-c("firebrick4",#"firebrick3","firebrick2",
           "firebrick1",#"mediumvioletred",
             "dodgerblue1",#"dodgerblue2","dodgerblue3",
           "dodgerblue4")
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen2AFIConcor_3

dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsOutcomes<-dsOutcomes[!is.na(dsOutcomes$SubjectTag),]
ds2D <-dsOutcomes#
max_val <- max(abs(ds2D$Intel_G1),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))
##############
ggplot(ds2D, aes(y=AFI_G2, x=Intel_G2,colour=(Intel_G1))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.01, h = 0.5)) +
  scale_color_gradientn(values=values,rescaler = function(x, ...) x, oob = identity,name="Gen1 \nAFQT",colours=shading)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=16,face="bold"))+ 
  ylab("Gen2 Age at First Intercourse") +
  xlab("Gen2 General Cognitive Ability") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")
@
\end{center}
\end{minipage}\end{landscape}
%
% Within-Family
\subsection{Within-Family Analyses}
\input{../Common/content/writing/results_within.tex}
%
\begin{landscape}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 1: Age at First Intercourse vs. Intelligence}
\label{plot_gen1_afi}
\begin{center}
<<plot_gen1_afi,fig=TRUE,echo=FALSE,cache=TRUE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
library(ggplot2)
library(gtable)
library(grid)
library(gridExtra)
library(NlsyLinks)
# Gen 1 Plot
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen1AFIConcor
dsOutcomes$Sex<-testretest$SEX
dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsD <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c("Intel_G1","AFI_G1","Sex"))
dsD$DIF_G<-#abs
  (dsD$Intel_G1_S1-dsD$Intel_G1_S2)
dsD$DIF_A<-#abs
  (dsD$AFI_G1_S1-dsD$AFI_G1_S2)
#m<-data.frame(Gen2AFIConcor$Intel_G2,Gen2AFIConcor$AFI_G2)

#shading<-c("navy","dodgerblue4","dodgerblue3","dodgerblue2","lightsteelblue1","dodgerblue2","dodgerblue3","dodgerblue4","navy")
shading<-c("firebrick4",#"firebrick3","firebrick2",
           "firebrick1",#"mediumvioletred",
             "dodgerblue1",#"dodgerblue2","dodgerblue3",
           "dodgerblue4")
max_val <- max(abs(dsD$DIF_G),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))

dsD$density<-NA
dsD$density[dsD$DIF_G < .33]<- 0
dsD$density[dsD$DIF_G < -.33]<- -1
dsD$density[dsD$DIF_G >= .33]<- 1
dsD$density<-as.factor(dsD$density)

### Marginal Density Plot y
ydensity <- ggplot(dsD, aes(x=AFI_G1_S1, group=density, color=density)) + 
  geom_density(fill=NA,adjust=2)+
  scale_colour_manual(values= c("firebrick1", "#AD78B6", "dodgerblue1"))+
  coord_cartesian(ylim=c(0,0.25), xlim=c(12,25))+
  theme_min(size=8)+ 
  theme(legend.position = "none",
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
   plot.margin=unit(c(0,0,.35,-.5), "cm"))+
  coord_flip()
### Marginal Density Plot x

xdensity <- ggplot(dsD, aes(x=Intel_G1_S1, group=density, color=density)) +
  geom_density(fill=NA,adjust=2) +
  scale_colour_manual(values= c("firebrick1", "#AD78B6", "dodgerblue1"))+ 
  theme_min(size=8) +
  theme(legend.position = "none",axis.title.y = element_blank(),
                            axis.title.x = element_blank(),
                            axis.text.x = element_blank(),
   plot.margin=unit(c(0,0,-.5,2.8), "cm"))

### Scatter plot
main<- ggplot(dsD, aes(y=AFI_G1_S1, x=Intel_G1_S1,colour=(DIF_G))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.1, h = 0.5)) +
  scale_colour_gradientn(name="Gen1 \nSibling \nDifferences \nin AFQT",colours=shading,values=values,rescaler = function(x, ...) x, oob = identity)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=12),
   plot.margin=unit(c(0,0.01,0,-.5), "cm"),
   legend.position="left",
   legend.key.width=unit(.5,"cm"))+ 
  ylab("Gen1 Age at First Intercourse") +
  xlab("Gen1 AFQT (Z Score)") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")

blankPlot <- ggplot()+geom_blank(aes(1,1))+
  theme(plot.background = element_blank(), 
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(), 
   panel.border = element_blank(),
   panel.background = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_blank(),
   axis.text.x = element_blank(), 
   axis.text.y = element_blank(),
   axis.ticks = element_blank(),
   plot.margin=unit(c(0,0,0,0), "cm"))

grid.arrange(xdensity, blankPlot,
             main, ydensity, ncol=2, nrow=2,widths=c(4, 1), heights=c(1, 4))
@
\end{center}\end{minipage}\end{landscape}

%%%%%%%%%%%% Discussion %%%%%%%%%%%%
\section{Discussion}
\input{../Common/content/writing/discussion.tex}
%%%%%%%%%%%% References %%%%%%%%%%%%
\bibliography{Projects-AFI}
%%%%%%%%%%%% Appendix %%%%%%%%%%%%
   \begin{landscape} \appendix\label{appen}
  %
  % Age 10.5 Replication
  \section{Age 10.5 Replication}\label{appen10}
  %% Between-Family

@@

\end{document}
